---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# baskwrap

<!-- badges: start -->

<!-- badges: end -->

The baskwrap package supplies a unified wrapper to several basket trial packages (`basksim` and `baskexact`) using a unified syntax.

## Installation

You can install the development version of baskwrap from [GitHub](https://github.com/LukasDSauer/baskwrap) with:

``` r
# install.packages("pak")
pak::pak("LukasDSauer/baskwrap")
```

## Example

The baskwrap package provides a simple interface to switch between two methods for calculating basket trial characteristics, numerical integration ("exact") and Monte Carlo simulation ("simulated").

```{r example}
library(baskwrap)
# INPUT PARAMETERS
n <- 20
p1 <- c(0.2, 0.5, 0.5)
lambda <- 0.95
epsilon <- 2
tau <- 0.5
design <- setup_fujikawa_x(k = 3, p0 = 0.2, backend = "exact")
# DETAILS USING EXACT BACKEND
get_details(design = design, n = n, p1 = p1, lambda = lambda,
            epsilon = epsilon, tau = tau)
# DETAILS USING MC BACKEND
get_details(design = set_backend(design, "sim"),
            n = n, p1 = p1, lambda = lambda,
            epsilon = epsilon, tau = tau)
```
